Estimating duration in the presence of misclassification

### 2024-03-19 biology-data.tex
ch 2 intro

\todo[inline]{Rewrite chapter 2 intro after writing thesis intro because it will be clearer how to divide content.}

SARS-CoV-2 is a beta coronavirus that emerged in late 2019.
It is closely related to previous coronaviruses that have caused outbreaks in humans, SARS-CoV and MERS-CoV.

Coronaviruses are RNA (Ribonucleic acid) viruses.
RNA viruses use RNA, rather than DNA, as their genetic material.

@@

\section{Studies used in this thesis} \label{biology-data:sec:studies}

In this section, I expand on the major two studies I use in this thesis (ATACCC and CIS).
Unlike many studies of SARS-CoV-2, these studies are not focused on specific groups such as healthcare workers or hospital patients.
Therefore, the results from these studies are more generalisable to the entire UK population.

\subsection{Assessment of Transmission and Contagiousness of COVID-19 in Contacts} \label{biology-data:sec:ataccc}

@@

\subsection{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

@@

\subsubsection{Strata} \label{biology-data:sec:cis-strata}

@@

\subsubsection{Adjustment for non-response and data sparsity} \label{biology-data:sec:MRP}

@@

\subsubsection{Clustering} \label{biology-data:sec:clustering}

@@

\subsubsection{Positivity results} \label{biology-data:sec:positivity-results}

@@

\subsubsection{Episodes} \label{biology-data:sec:cis-episodes}

@@

\subsubsection{Computational limitations and privacy protection} \label{biology-data:sec:SRS}

>>>>

SARS-CoV-2 is closely related to previous coronaviruses that have caused outbreaks in humans, SARS-CoV and MERS-CoV.
Coronaviruses are RNA (Ribonucleic acid) viruses.
RNA viruses use RNA, rather than DNA, as their genetic material.
RNA viruses, which include influenza, mutate rapidly and are the most likely class of viruses to cause pandemics~\autocite{woolhouseRNA}.

The initial and most sensitive diagnostic test for SARS-CoV-2 uses RT-PCR, which I explain in \cref{biology-data:sec:PCR}.
SARS-CoV-2 causes the disease COVID-19; I discuss the \emph{natural history} of the disease, the course it takes from beginning to end~\autocite[193]{portaEpiDictionary}, in \cref{biology-data:sec:natural-history}.

I then move on to discussing the two studies I use in this thesis.
These are ATACCC (\cref{biology-data:sec:ataccc}) and the CIS (\cref{intro:sec:cis}), both briefly discussed in \cref{E-intro}.
Unlike many studies of SARS-CoV-2, these studies are not focused on specific groups such as healthcare workers or hospital patients.
Therefore, the results from these studies are more generalizable to the entire UK population.

@@

% \section{Studies used ie this thesis} \label{biology-data:sec:studies}

% In this section, I expand on the major two studies I use in this thesis (ATACCC and CIS).
% Unlike many studies of SARS-CoV-2, these studies are not focused on specific groups such as healthcare workers or hospital patients.
% Therefore, the results from these studies are more generalisable to the entire UK population.

\section{Assessment of Transmission and Contagiousness of COVID-19 in Contacts} \label{biology-data:sec:ataccc}

@@

\section{Coronavirus (COVID-19) Infection Survey} \label{intro:sec:cis}

@@

\subsection{Strata} \label{biology-data:sec:cis-strata}

@@

\subsection{Adjustment for non-response and data sparsity} \label{biology-data:sec:MRP}

@@

\subsection{Clustering} \label{biology-data:sec:clustering}

@@

\subsection{Positivity results} \label{biology-data:sec:positivity-results}

@@

\subsection{Episodes} \label{biology-data:sec:cis-episodes}

@@

\subsection{Computational limitations and privacy protection} \label{biology-data:sec:SRS}
